Parameter Recovery Validation

### 2025-05-29 nbs/concepts/parameter-recovery-validation/index.qmd
feat(plots): add automatic PNG/PDF saving to predictive check plots
- Add save_path and figure_name parameters to plot_prior_predictive_checks()
- Add save_path and figure_name parameters to plot_posterior_predictive_checks()
- Implement automatic directory creation with os.makedirs(exist_ok=True)
- Save both PNG and PDF formats with high DPI (300) and tight bounding box
- Add informative print statements showing saved file paths
- Update documentation to demonstrate save functionality
- Fix Unicode characters in plot labels to avoid LaTeX rendering issues
- Test save functionality with tempor

# PyroVelocity imports
from pyrovelocity.models.modular.factory import create_piecewise_activation_model
# from pyrovelocity.plots.piecewise import (
#     plot_piecewise_phase_portrait,
#     plot_piecewise_trajectories,
#     plot_activation_timing,
# )
# from pyrovelocity.plots.predictive_checks import (
#     plot_prior_predictive_checks,
#     plot_posterior_predictive_checks,
#     plot_parameter_recovery_diagnostics,
# )

@@

# Plot prior predictive checks
fig_prior = plot_prior_predictive_checks(
    model=model,
    prior_adata=prior_predictive_adata,
    prior_parameters=prior_parameter_samples,
    figsize=(15, 10)
)

>>>>

# PyroVelocity imports
from pyrovelocity.models.modular.factory import create_piecewise_activation_model
# from pyrovelocity.plots.piecewise import (
#     plot_piecewise_phase_portrait,
#     plot_piecewise_trajectories,
#     plot_activation_timing,
# )
from pyrovelocity.plots.predictive_checks import (
    plot_prior_predictive_checks,
    plot_posterior_predictive_checks,
)
# from pyrovelocity.plots.parameter_recovery import (
#     plot_parameter_recovery_diagnostics,
# )

@@

# Plot prior predictive checks with automatic saving
# This will save both PNG and PDF copies to reports/docs/prior_predictive/
fig_prior = plot_prior_predictive_checks(
    model=model,
    prior_adata=prior_predictive_adata,
    prior_parameters=prior_parameter_samples,
    figsize=(15, 10),
    save_path="reports/docs/prior_predictive",
    figure_name="piecewise_activation_prior_checks"
)
